---
title: "HW5"
author: "Soungbin Yim"
date: "2022-11-15"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(p8105.datasets)
library(viridis)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))
```


### Due date

Due: November 16 at 11:59pm. 

### Points

| Problem         | Points    |
|:--------------- |:--------- |
| Problem 0       | 20        |
| Problem 1       | --        |
| Problem 2       | 40        |
| Problem 3       | 40        |
| Optional survey | No points |


### Problem 0

This "problem" focuses on structure of your submission, especially the use git and GitHub for reproducibility, R Projects to organize your work, R Markdown to write reproducible reports, relative paths to load data from local files, and reasonable naming structures for your files. This was not prepared as a GitHub repo.

```{r load_libraries}
library(tidyverse)
```

## Problem 2

```{r}
homicide_df =
  read_csv("./homicide-data.csv") %>%
  mutate(
    victim_age = as.numeric(victim_age),
    city_state = str_c(city, ", ", state)
  ) %>%
  group_by(city_state) %>%
  summarize(unsolved_sum = sum(disposition == "Closed without arrest", disposition == "Open/No arrest"),
    total_homicide = n()) 

baltimore_df = 
  homicide_df %>%
  filter(city_state %in% c("Baltimore, MD"))

Prop_baltimore_df =
  prop.test(baltimore_df$unsolved_sum,baltimore_df$total_homicide,
    alternative = c("two.sided"),
    conf.level = 0.95, correct = TRUE) %>%
  broom::tidy()

Prop_baltimore_df %>%
  select(estimate, "CI_lower" = conf.low, "CI_upper" = conf.high)

 prop.test(homicide_df$unsolved_sum,homicide_df$total_homicide,
    alternative = c("two.sided"),
    conf.level = 0.95, correct = TRUE) %>%
  broom::tidy()
 
prop_homicide_df =
  homicide_df %>%
  mutate(proportion = purrr::map2(unsolved_sum,total_homicide,prop.test),
         proportion = purrr::map(proportion, broom::tidy)) %>%
  unnest(proportion) %>%
  select(1:4,8,9)

prop_homicide_df %>% 
  ggplot(aes(reorder(city_state,estimate), estimate)) +       
  geom_point(aes(color = city_state)) +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
    labs(
    title = "Problem 2, plot of unsolved homicide proportion estimates and CIs for each city ",
    x = "City, State",
    y = "Proportion Estimate") +
   theme(axis.text.x = element_text(angle = 90),
         legend.position = "none")

```
## Problem 3
When designing an experiment or analysis, a common question is whether it is likely that a true effect will be detected – put differently, whether a false null hypothesis will be rejected. The probability that a false null hypothesis is rejected is referred to as power, and it depends on several factors, including: the sample size; the effect size; and the error variance. In this problem, you will conduct a simulation to explore power in a one-sample t-test.

First set the following design elements:

Fix n=30
Fix σ=5
Set μ=0. Generate 5000 datasets from the model

x∼Normal[μ,σ]

For each dataset, save μ^ and the p-value arising from a test of H:μ=0 using α=0.05. Hint: to obtain the estimate and p-value, use broom::tidy to clean the output of t.test.

Repeat the above for μ={1,2,3,4,5,6}, and complete the following:

Make a plot showing the proportion of times the null was rejected (the power of the test) on the y axis and the true value of μ on the x axis. Describe the association between effect size and power.
Make a plot showing the average estimate of μ^ on the y axis and the true value of μ on the x axis. Make a second plot (or overlay on the first) the average estimate of μ^ only in samples for which the null was rejected on the y axis and the true value of μ on the x axis. Is the sample average of μ^ across tests for which the null is rejected approximately equal to the true value of μ? Why or why not?###

#### Generating the dataset
```{r}
sim_ttest = function(mu, n=30, sigma=5) {
  
  sim_data = tibble(
    x = rnorm(n = n, mean = mu, sd = sigma),
  )
  
  sim_data =
  t.test(sim_data) %>%
  broom::tidy() %>%
  select(estimate, p.value)
}

sim_results_df = 
  expand_grid(
    mu = 0, 
    iter = 1:5000
  ) %>% 
  mutate(
    estimate_df = map(mu, sim_ttest)
  ) %>% 
  unnest(estimate_df)

```
```{r}
sim_ttest = function(mu, n=30, sigma=5) {
  
  sim_data = tibble(
    x = rnorm(n = n, mean = mu, sd = sigma),
  )
  
  sim_data =
  t.test(sim_data) %>%
  broom::tidy() %>%
  select(estimate, p.value)
}

sim_results_df2 = 
  expand_grid(
    mu = 1:6, 
    iter = 1:5000
  ) %>% 
  mutate(
    estimate_df = map(mu, sim_ttest)
  ) %>% 
  unnest(estimate_df)
```
## Make a plot showing the proportion of times the null was rejected (the power of the test) on the y axis and the true value of μ on the x axis. Describe the association between effect size and power.
```{r}
sim_results_df2 %>% 
  group_by(mu) %>%
  summarize(reject = (sum(p.value < 0.05))/n()) %>%
  ggplot(aes(x = mu, y = reject)) + 
  geom_point(colour = "green") +
  geom_line() +
  scale_x_continuous(breaks = seq(0,6, by = 1)) +
    labs(
    title = "Problem 3, First plot",
    x = "The true value of μ",
    y = "The proportion of times the null was rejected (Power)") +
   theme(legend.position = "none")
```
## Make a plot showing the average estimate of μ^ on the y axis and the true value of μ on the x axis. Make a second plot (or overlay on the first) the average estimate of μ^ only in samples for which the null was rejected on the y axis and the true value of μ on the x axis. Is the sample average of μ^ across tests for which the null is rejected approximately equal to the true value of μ? Why or why not?

```{r}


```

