---
title: "HW5"
author: "Soungbin Yim"
date: "2022-11-15"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(p8105.datasets)
library(viridis)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))
```


### Due date

Due: November 16 at 11:59pm. 

### Points

| Problem         | Points    |
|:--------------- |:--------- |
| Problem 0       | 20        |
| Problem 1       | --        |
| Problem 2       | 40        |
| Problem 3       | 40        |
| Optional survey | No points |


### Problem 0

This "problem" focuses on structure of your submission, especially the use git and GitHub for reproducibility, R Projects to organize your work, R Markdown to write reproducible reports, relative paths to load data from local files, and reasonable naming structures for your files. This was not prepared as a GitHub repo.

```{r load_libraries}
library(tidyverse)
```

## Problem 2
Describe the raw data. Create a city_state variable (e.g. “Baltimore, MD”) and then summarize within cities to obtain the total number of homicides and the number of unsolved homicides (those for which the disposition is “Closed without arrest” or “Open/No arrest”).

```{r}
homicide_df =
  read_csv("./homicide-data.csv") %>%
  mutate(
    victim_age = recode(victim_age,"Unknown" = ""),
    victim_age = as.numeric(victim_age),
    city_state = str_c(city, ", ", state)
  ) %>%
  group_by(city_state) %>%
  summarize(unsolved_sum = sum(disposition == "Closed without arrest", disposition == "Open/No arrest"),
    total_homicide = n()) 
```

The raw data has ``r nrow(homicide_df)`` observations and ``r ncol(homicide_df)`` variables. The `victim_age` variable had some missing observations with `Unknown`, so I substituted with `NA` and changed the variable as numeric with `as.numeric`.
  
The following table shows the total number of homicides and the number of unsolved homicides for each city: `r homicide_df %>% knitr::kable()`

For the city of Baltimore, MD, use the prop.test function to estimate the proportion of homicides that are unsolved; save the output of prop.test as an R object, apply the broom::tidy to this object and pull the estimated proportion and confidence intervals from the resulting tidy dataframe.
```{r}
baltimore_df = 
  homicide_df %>%
  filter(city_state %in% c("Baltimore, MD"))

Prop_baltimore_df =
  prop.test(baltimore_df$unsolved_sum,baltimore_df$total_homicide,
    alternative = c("two.sided"),
    conf.level = 0.95, correct = TRUE) %>%
  broom::tidy()

Prop_baltimore_df %>%
  select(estimate, "CI_lower" = conf.low, "CI_upper" = conf.high)
```

Now run prop.test for each of the cities in your dataset, and extract both the proportion of unsolved homicides and the confidence interval for each. Do this within a “tidy” pipeline, making use of purrr::map, purrr::map2, list columns and unnest as necessary to create a tidy dataframe with estimated proportions and CIs for each city.
```{r}
 prop.test(homicide_df$unsolved_sum,homicide_df$total_homicide,
    alternative = c("two.sided"),
    conf.level = 0.95, correct = TRUE) %>%
  broom::tidy()
 
prop_homicide_df =
  homicide_df %>%
  mutate(proportion = purrr::map2(unsolved_sum,total_homicide,prop.test),
         proportion = purrr::map(proportion, broom::tidy)) %>%
  unnest(proportion) %>%
  select(1:4,8,9)
```

The estimated proportions and CIs for each city: `r prop_homicide_df %>% knitr::kable()`.

Create a plot that shows the estimates and CIs for each city – check out geom_errorbar for a way to add error bars based on the upper and lower limits. Organize cities according to the proportion of unsolved homicides.
```{r}
prop_homicide_df %>% 
  ggplot(aes(reorder(city_state,estimate), estimate)) +       
  geom_point(aes(color = city_state)) +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
    labs(
    title = "Problem 2, plot of unsolved homicide proportion estimates and CIs for each city ",
    x = "City, State",
    y = "Proportion Estimate") +
   theme(axis.text.x = element_text(angle = 90),
         legend.position = "none")
```

## Problem 3

When designing an experiment or analysis, a common question is whether it is likely that a true effect will be detected – put differently, whether a false null hypothesis will be rejected. The probability that a false null hypothesis is rejected is referred to as power, and it depends on several factors, including: the sample size; the effect size; and the error variance. In this problem, you will conduct a simulation to explore power in a one-sample t-test.

First set the following design elements:

Fix n=30
Fix σ=5
Set μ=0. Generate 5000 datasets from the model

x∼Normal[μ,σ]

For each dataset, save μ^ and the p-value arising from a test of H:μ=0 using α=0.05. Hint: to obtain the estimate and p-value, use broom::tidy to clean the output of t.test.

Repeat the above for μ={1,2,3,4,5,6}

#### Generating the dataset
```{r}
sim_ttest = function(mu, n=30, sigma=5) {
  sim_data = tibble(
    x = rnorm(n = n, mean = mu, sd = sigma),
  )
  sim_data =
  t.test(sim_data) %>%
  broom::tidy() %>%
  select(estimate, p.value)
}
sim_results_df = 
  expand_grid(
    mu = 0, 
    iter = 1:5000
  ) %>% 
  mutate(
    estimate_df = map(mu, sim_ttest)
  ) %>% 
  unnest(estimate_df)
```
```{r}
sim_ttest = function(mu, n=30, sigma=5) {
  sim_data = tibble(
    x = rnorm(n = n, mean = mu, sd = sigma),
  )
  sim_data =
  t.test(sim_data) %>%
  broom::tidy() %>%
  select(estimate, p.value)
}
sim_results_df2 = 
  expand_grid(
    mu = 1:6, 
    iter = 1:5000
  ) %>% 
  mutate(
    estimate_df = map(mu, sim_ttest)
  ) %>% 
  unnest(estimate_df)
```

Make a plot showing the proportion of times the null was rejected (the power of the test) on the y axis and the true value of μ on the x axis. Describe the association between effect size and power.
```{r}
sim_results_df2 %>% 
  group_by(mu) %>%
  summarize(reject = sum(p.value < 0.05)/n()) %>%
  ggplot(aes(x = mu, y = reject)) + 
  geom_point(colour = "green") +
  geom_line() +
  scale_x_continuous(breaks = seq(1,6, by = 1)) +
    labs(
    title = "Problem 3, First plot, the proportion of times the null was rejected vs. True value of μ ",
    x = "The true value of μ",
    y = "The proportion of times the null was rejected (Power)") +
   theme(legend.position = "none")
```

From the plot above, we can observe a clear positive relationship between the effect size and power, meaning power increases as effect size increases. However, as power approaches 1, especially after mu=3, the slope gets less steeper, meaning effect size would have diminishing returns.

Make a plot showing the average estimate of μ^ on the y axis and the true value of μ on the x axis. Make a second plot (or overlay on the first) the average estimate of μ^ only in samples for which the null was rejected on the y axis and the true value of μ on the x axis. Is the sample average of μ^ across tests for which the null is rejected approximately equal to the true value of μ? Why or why not?

```{r}
sim_results_df2 %>% 
  group_by(mu) %>% 
  summarize(mean = mean(estimate)) %>%
  ggplot(aes(x = mu, y = mean)) +
  geom_point() +
  geom_line(color = "Red") +
  labs(
   title = "Problem 3, Second plot, average estimate of μ of full sample",
   x = "True value of μ",
   y = "Average estimate of μ") + 
  scale_x_continuous(breaks = seq(1,6,by = 1))

sim_results_df2 %>% 
  filter(p.value < 0.05) %>% 
  group_by(mu) %>% 
  summarize(mean = mean(estimate)) %>%
ggplot(aes(x = mu, y = mean)) +
  geom_point() +
  geom_line(color = "Blue") +
  labs(
   title = "Problem 3, Third plot, average estimate of μ of sample with rejected null",
   x = "True value of μ",
   y = "Average estimate of μ" + 
  scale_x_continuous(breaks = seq(1,6,by = 1)))
```

The sample average of μ^ across tests for which the null is rejected is not approximately equal to the true value of μ. At lower true values of μ, the average estimate of μ of sample with rejected null has higher value compared to average estimate μ of full sample. The sample average of estimated μ across tests for which the null is rejected is not approximately equal to the true value of μ . They become approximately equal at larger true values of μ. The slight differences at lower true values of μ are caused by the lower power at lower true values of μ. Not all samples are correctly rejected at lower power, causing the mean μ to deviated from the true values of μ.
